---
title: "MPM Group Project - AirBnb Price Prediction"
author: "Giedo, Micha, Azher, Christoph"
date: "4/25/2021"
output: html_document
---

In this report, our group analyses the influence of different predictors on the 
listing price of AirBnb offerings in different cites in the United States.

The final model should provide a way to estimate the correct price for any new or existing 
object listed on AirBnB in order to ensure high booking rates. Also, it ensures
users of this model to not underprice their object and lose out on improved margins.
Please keep in mind, this model does not take into consideration the exact location
or 'cleanness' of an object due to a lack of data. However, both of these predictors
would have a high influence. Meaning, you apartment most likely still 
needs to be clean to result in a high booking rate

First we will take a deeper look at our data, the response variable log_price 
and all the available predictors.

Lets look at all the predictors of our data set.

```{r, echo=FALSE}
df.airbnb <- read.csv("MPM_Prop.csv")
df.airbnb$property_type <- as.factor(df.airbnb$property_type)
df.airbnb$room_type <- as.factor(df.airbnb$room_type)
df.airbnb$bed_type <- as.factor(df.airbnb$bed_type)
df.airbnb$cancellation_policy <- as.factor(df.airbnb$cancellation_policy)
df.airbnb$cleaning_fee <- as.factor(df.airbnb$cleaning_fee)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$host_has_profile_pic <- as.factor(df.airbnb$host_has_profile_pic)
df.airbnb$host_identity_verified <- as.factor(df.airbnb$host_identity_verified)
df.airbnb$instant_bookable <- as.factor(df.airbnb$instant_bookable)
df.airbnb$amenities_Breakfast <- as.factor(df.airbnb$amenities_Breakfast)
df.airbnb$amenities_Gym <- as.factor(df.airbnb$amenities_Gym)
df.airbnb$amenities_Pets <- as.factor(df.airbnb$amenities_Pets)
df.airbnb$amenities_WiFi <- as.factor(df.airbnb$amenities_WiFi)
colnames(df.airbnb)
```

We can see, our data set consists of a response variable and 19 predictors.
With a few simple commands, a better understanding of the values can be gained.

```{r}
head(df.airbnb)
```
Head provides an overview over the first 5 entries in the table, this provides
us with some knowledge about how the rows look.

```{r}
summary(df.airbnb)
``` 

The summary() command provides a first statistical overview of the data.

```{r}
str(df.airbnb)
`````

And str() indicates the type of the variables.
Form this we can conclude, our target variable is a continuous variable, as 
predictors we have one continuous variable (number_of_reviews), 13 categorical
variables most with two levels but also some with five or 6, one binomial
variable (review_scores_rating) and four count variables.

## Applying the Possion Distribution

As our response variable is a continuous variable, we cannot apply the Poisson distribution
to it. To show how this would work, we are going to consider another variable as our response variable.

For this example, we choose the variable 'accommodates' where we want to find out if some predictors
influence the size of the object to rent. Obviously, this is pretty clear for some predictors. If 
the object accommodates more there are most likely to be more beds. Hence this should really only be
regarded as an example of applying the Possion distribution.






## Applying the Binomial Distribution






## Running Cross Validation Checks on the models
