---
title: "MPM Group Project - AirBnb Price Prediction"
author: "Giedo, Micha, Azher, Christoph"
date: "4/25/2021"
output: html_document
---

In this report, our group analyses the influence of different predictors on the 
listing price of AirBnb offerings in different cites in the United States.

First we will take a deeper look at our data, the response variable log_price 
and all the available predictors.

Lets look at all the predictors of our data set.

```{r, echo=FALSE}
df.airbnb <- read.csv("MPM_Prop.csv")
df.airbnb$property_type <- as.factor(df.airbnb$property_type)
df.airbnb$room_type <- as.factor(df.airbnb$room_type)
df.airbnb$bed_type <- as.factor(df.airbnb$bed_type)
df.airbnb$cancellation_policy <- as.factor(df.airbnb$cancellation_policy)
df.airbnb$cleaning_fee <- as.factor(df.airbnb$cleaning_fee)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$host_has_profile_pic <- as.factor(df.airbnb$host_has_profile_pic)
df.airbnb$host_identity_verified <- as.factor(df.airbnb$host_identity_verified)
df.airbnb$instant_bookable <- as.factor(df.airbnb$instant_bookable)
df.airbnb$amenities_Breakfast <- as.factor(df.airbnb$amenities_Breakfast)
df.airbnb$amenities_Gym <- as.factor(df.airbnb$amenities_Gym)
df.airbnb$amenities_Pets <- as.factor(df.airbnb$amenities_Pets)
df.airbnb$amenities_WiFi <- as.factor(df.airbnb$amenities_WiFi)
colnames(df.airbnb)
```

We can see, our data set consists of a response variable and 19 predictors.
With a few simple commands, a better understanding of the values can be gained.

```{r}
head(df.airbnb)
```
Head provides an overview over the first 5 entries in the table, this provides
us with some knowledge about how the rows look.

```{r}
summary(df.airbnb)
``` 

The summary() command provides a first statistical overview of the data.

```{r}
str(df.airbnb)
`````

And str() indicates the type of the variables.
Form this we can conclude, our target variable is a continuous variable, as 
predictors we have one continuous variable (number_of_reviews), 13 categorical
variables most with two levels but also some with five or 6, one binomial
variable (review_scores_rating) and four count variables.

