---
title: "SVM"
author: "Giedo, Micha, Azher, Christoph"
date: "6/11/2021"
output: html_document
---

```{r include=FALSE}

library(e1071)
library(ggplot2)
library(plyr)
library(multcomp)
library(splines)
library(faraway)
library(dplyr)
library(caret)
library(tidyverse)
library(neuralnet)
library(nnet)
library(gamlss.add)
library(ggplot2)
library(mgcv)
library(caret)
library(tidyverse)
library(abc)

df.airbnb <- read.csv("MPM_Last_.csv")
df.airbnb.num <- read.csv("MPM_Prop.csv")

df.airbnb$property_type <- as.factor(df.airbnb$property_type)
df.airbnb$room_type <- as.factor(df.airbnb$room_type)
df.airbnb$bed_type <- as.factor(df.airbnb$bed_type)
df.airbnb$cancellation_policy <- as.factor(df.airbnb$cancellation_policy)
df.airbnb$cleaning_fee <- as.factor(df.airbnb$cleaning_fee)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$city <- as.factor(df.airbnb$city)
df.airbnb$host_has_profile_pic <- as.factor(df.airbnb$host_has_profile_pic)
df.airbnb$host_identity_verified <- as.factor(df.airbnb$host_identity_verified)
df.airbnb$instant_bookable <- as.factor(df.airbnb$instant_bookable)
df.airbnb$amenities_Breakfast <- as.factor(df.airbnb$amenities_Breakfast)
df.airbnb$amenities_Gym <- as.factor(df.airbnb$amenities_Gym)
df.airbnb$amenities_Pets <- as.factor(df.airbnb$amenities_Pets)
df.airbnb$amenities_WiFi <- as.factor(df.airbnb$amenities_WiFi)

df.airbnb.num$property_type <- as.factor(df.airbnb.num$property_type)
df.airbnb.num$room_type <- as.factor(df.airbnb.num$room_type)
df.airbnb.num$bed_type <- as.factor(df.airbnb.num$bed_type)
df.airbnb.num$cancellation_policy <- as.factor(df.airbnb.num$cancellation_policy)
df.airbnb.num$cleaning_fee <- as.factor(df.airbnb.num$cleaning_fee)
df.airbnb.num$city <- as.factor(df.airbnb.num$city)
df.airbnb.num$city <- as.factor(df.airbnb.num$city)
df.airbnb.num$host_has_profile_pic <- as.factor(df.airbnb.num$host_has_profile_pic)
df.airbnb.num$host_identity_verified <- as.factor(df.airbnb.num$host_identity_verified)
df.airbnb.num$instant_bookable <- as.factor(df.airbnb.num$instant_bookable)
df.airbnb.num$amenities_Breakfast <- as.factor(df.airbnb.num$amenities_Breakfast)
df.airbnb.num$amenities_Gym <- as.factor(df.airbnb.num$amenities_Gym)
df.airbnb.num$amenities_Pets <- as.factor(df.airbnb.num$amenities_Pets)
df.airbnb.num$amenities_WiFi <- as.factor(df.airbnb.num$amenities_WiFi)

df.airbnb$price <- 3^df.airbnb$log_price
df.airbnb.num$price <- 3^df.airbnb.num$log_price

# The last calculation in the r snippet above applies the backtransformation of the log_price
# variable (log base 3) to provide a better picture of the actual prices for a user.
```

# Applying Support Vector Machines

```{r, include = FALSE}
df.airbnb.withoutcat <- read.csv("MPM_Prop.csv")

df.airbnb.withoutcat$property_type <- as.factor(df.airbnb.withoutcat$property_type)
df.airbnb.withoutcat$room_type <- as.factor(df.airbnb.withoutcat$room_type)
df.airbnb.withoutcat$bed_type <- as.factor(df.airbnb.withoutcat$bed_type)
df.airbnb.withoutcat$cancellation_policy <- as.factor(df.airbnb.withoutcat$cancellation_policy)
df.airbnb.withoutcat$cleaning_fee <- as.factor(df.airbnb.withoutcat$cleaning_fee)
df.airbnb.withoutcat$city <- as.factor(df.airbnb.withoutcat$city)
df.airbnb.withoutcat$city <- as.factor(df.airbnb.withoutcat$city)
df.airbnb.withoutcat$host_has_profile_pic <- as.factor(df.airbnb.withoutcat$host_has_profile_pic)
df.airbnb.withoutcat$host_identity_verified <- as.factor(df.airbnb.withoutcat$host_identity_verified)
df.airbnb.withoutcat$instant_bookable <- as.factor(df.airbnb.withoutcat$instant_bookable)
df.airbnb.withoutcat$amenities_Breakfast <- as.factor(df.airbnb.withoutcat$amenities_Breakfast)
df.airbnb.withoutcat$amenities_Gym <- as.factor(df.airbnb.withoutcat$amenities_Gym)
df.airbnb.withoutcat$amenities_Pets <- as.factor(df.airbnb.withoutcat$amenities_Pets)
df.airbnb.withoutcat$amenities_WiFi <- as.factor(df.airbnb.withoutcat$amenities_WiFi)
```

Although SVM can not be applied to the response variable log_price of this group work, we still try to use this technique in two of the following cases.

Case 1: We classify "review_scores_rating" into two classes that are above or below median rating.
```{r}
summary(df.airbnb.withoutcat$review_scores_rating)
df.airbnb.withoutcat$isAboveorBelowRating <- 0
for(i in 1:73470 ) {
  if (df.airbnb.withoutcat$review_scores_rating[as.integer(i)] > 94) {
    df.airbnb.withoutcat$isAboveorBelowRating[i] <- 1
  } else {
    df.airbnb.withoutcat$isAboveorBelowRating[i] <- 0
  }
}
df.airbnb.withoutcat$isAboveorBelowRating <- as.factor(df.airbnb.withoutcat$isAboveorBelowRating)
```

Case 2: In this case, we classify log_price into two classes that are above or below median price.
```{r}
summary(df.airbnb.withoutcat$log_price)
df.airbnb.withoutcat$isAboveorBelowPrice <- 0
for(i in 1:73470 ) {
  if (df.airbnb.withoutcat$log_price[as.numeric(i)] > 4.7) {
    df.airbnb.withoutcat$isAboveorBelowPrice[i] <- 1
  } else {
    df.airbnb.withoutcat$isAboveorBelowPrice[i] <- 0
  }
}
df.airbnb.withoutcat$isAboveorBelowPrice <- as.factor(df.airbnb.withoutcat$isAboveorBelowPrice)

```

Let us plot classified review_scores_rating data.
```{r}
df.airbnb.withoutcat %>%
  ggplot(aes(x = number_of_reviews, y = log_price, color = isAboveorBelowRating)) + geom_point() + facet_wrap(. ~ city)
```

Similarly, let us plot classified log_price data.
```{r}
df.airbnb.withoutcat %>%
  ggplot(aes(x = number_of_reviews, y = review_scores_rating, color = isAboveorBelowPrice)) + 
  geom_point() + facet_wrap(. ~ city)

```

Let us prepare data for training.
```{r}
str(df.airbnb.withoutcat)
set.seed(222)
indices_Rating <- createDataPartition(df.airbnb.withoutcat$isAboveorBelowRating, p=.8, list = F)

train_Rating <- df.airbnb.withoutcat %>% slice(indices_Rating)
test_in_Rating <- df.airbnb.withoutcat %>% slice(-indices_Rating) %>% select(-isAboveorBelowRating)
test_truth_Rating <- df.airbnb.withoutcat %>% slice(-indices_Rating) %>% pull(isAboveorBelowRating)

set.seed(222)
indices_Price <- createDataPartition(df.airbnb.withoutcat$isAboveorBelowPrice, p=.8, list = F)

train_Price <- df.airbnb.withoutcat %>% slice(indices_Price)
test_in_Price <- df.airbnb.withoutcat %>% slice(-indices_Price) %>% select(-isAboveorBelowPrice)
test_truth_Price <- df.airbnb.withoutcat %>% slice(-indices_Price) %>% pull(isAboveorBelowPrice)
```

Let us apply a complex paramatier "radial" kernel to both cases.
```{r}
set.seed(222)
df.airbnb.withoutcat_svm_Rating1 <- svm(isAboveorBelowRating ~ ., train_Rating, kernel = "radial", scale = TRUE, cost = 100)
summary(df.airbnb.withoutcat_svm_Rating1)
plot(df.airbnb.withoutcat_svm_Rating1, train_Rating, review_scores_rating ~ number_of_reviews)

df.airbnb.withoutcat_svm_Price1 <- svm(isAboveorBelowPrice ~ ., train_Price, kernel = "radial", scale = TRUE, cost = 100)
summary(df.airbnb.withoutcat_svm_Price1)
plot(df.airbnb.withoutcat_svm_Price1, train_Price, log_price ~ number_of_reviews)
```

Let us make prediction.
```{r}
pred_Rating1 <- predict(df.airbnb.withoutcat_svm_Rating1, test_in_Rating)
table(pred_Rating1)
conf_matrix_Rating1 <- confusionMatrix(test_truth_Rating, pred_Rating1)
conf_matrix_Rating1

pred_Price1 <- predict(df.airbnb.withoutcat_svm_Price1, test_in_Price)
table(pred_Price1)
conf_matrix_Price1 <- confusionMatrix(test_truth_Price, pred_Price1)
conf_matrix_Price1
```
We can see that the prediction accuracy of case 1 is 99.88% and case 2 is 99.43% respectively.

Now let us apply "linear" kernel.
```{r}
df.airbnb.withoutcat_svm_Rating2 <- svm(isAboveorBelowRating ~ ., train_Rating, kernel = "linear", scale = TRUE, cost = 10)
summary(df.airbnb.withoutcat_svm_Rating2)
plot(df.airbnb.withoutcat_svm_Rating2, train_Rating, review_scores_rating ~ number_of_reviews)

df.airbnb.withoutcat_svm_Price2 <- svm(isAboveorBelowPrice ~ ., train_Price, kernel = "linear", scale = TRUE, cost = 10)
summary(df.airbnb.withoutcat_svm_Price2)
plot(df.airbnb.withoutcat_svm_Price2, train_Price, log_price ~ number_of_reviews)
```

Let us make a prediction through "linear" kernel.
```{r}
pred_Rating2 <- predict(df.airbnb.withoutcat_svm_Rating2, test_in_Rating)
table(pred_Rating2)
conf_matrix_Rating2 <- confusionMatrix(test_truth_Rating, pred_Rating2)
conf_matrix_Rating2

pred_Price2 <- predict(df.airbnb.withoutcat_svm_Price2, test_in_Price)
table(pred_Price2)
conf_matrix_Price2 <- confusionMatrix(test_truth_Price, pred_Price2)
conf_matrix_Price2
```
We see that the accuracy through "linear" kernel is very similar to the "radial" kernel in both cases (slight higher for Case 1 and lower for Case 2).

